---
title: "Group 13 - Final Project: Beijing"
author: "Study Group 13"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: minty
    highlight: breezedark
    number_sections: yes
    toc: yes
    toc_float: yes
    code_folding: show
---

#Change theme

```{r, setup, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
options(digits = 3)
# default figure size
knitr::opts_chunk$set(
  fig.width=6.75, 
  fig.height=6.75,
  fig.align = "center"
)
```

```{r load-libraries, include=FALSE}
#Using this space to load libraries
library(vroom)
library(dplyr)
library(knitr)
library(mosaic)
library(skimr)
library(ggplot2)
library(GGally)
library(janitor)
library(readr)
library(leaflet)
library(scales)
library(broom)
library(huxtable)
library(car)
library(ggfortify)
library(rsample)
library(ggridges)
library(patchwork)
library(kableExtra)
library(patchwork)
options('huxtable.knit_print_df' = FALSE)
```

# Studying the Beijing Airbnb Market

First we have to download the data.

```{r weather_data, cache=TRUE}
data <- vroom::vroom("listings.csv.gz") %>% 
  clean_names()
data
```

## Exploratory Data Analysis 

```{r}
# Lets have a look at what we're dealing with!
glimpse(data)
```
> From this output we can see that we have
* There are just over 36 thousand observations (or Airbnb listings) in Beijing in the data set
* There are 106 different variables included in the data
* These variables are a mixture of 'double', 'character', 'logic' and 'date'
* Straightaway we can see that some of our 'price' variables include dollar signs ($) and are down as 'character' variables rather than 'double' variables

Since this is a large data set with a lot going on, we will compute some summary statistics on key variables

```{r}
  listings <- data %>% 
  
  #Lets pick the variables we need
  select(c(price,
           cleaning_fee,
           extra_people,
           room_type,
           property_type,
           number_of_reviews,
           review_scores_rating,
           longitude,
           latitude,
           neighbourhood,
           minimum_nights,
           guests_included,
           bathrooms,
           bedrooms,
           beds,
           accommodates,
           host_is_superhost,
           neighbourhood_cleansed,
           cancellation_policy,
           listing_url,
           is_location_exact,
           security_deposit,
           review_scores_cleanliness,
           instant_bookable,
           is_business_travel_ready
           )
         ) %>% 

  #Removing dollar signs and changing into numerical variables
  mutate(
    price = parse_number(price),
    cleaning_fee = parse_number(cleaning_fee),
    extra_people = parse_number(extra_people),
    security_deposit = parse_number(security_deposit)
  )

listings
```


### Removing Missing Values
```{r}
# Check which variables have lots of missing values (NA's)
listings %>% 
  skim() %>% 
  kbl() %>% 
  kable_styling()

data_cleaned <- listings %>% 
  
  # Handling NA's
  mutate(
    cleaning_fee = case_when(
      is.na(cleaning_fee) ~ 0,
      TRUE ~ cleaning_fee
        ),
    security_deposit = case_when(
      is.na(security_deposit) ~ 0,
      TRUE ~ security_deposit
        )
    )

data_cleaned

data_cleaned %>% 
skim(cleaning_fee) %>% 
  kbl() %>% 
  kable_styling()
```

> Some properties do not have the cleaning fee separately because they include it in the rent price. This way, it is not seen as an "additional cost".
> #Psychology 

### Exploring Correlation Between Variables

```{r}

# Using patchwork to create a visualization of density for all numerical variables
p1 <- ggplot(data = cleaning, aes(x = price)) +
  geom_density() +
  theme_bw() 

p2 <- ggplot(data = cleaning, aes(x = cleaning_fee)) +
  geom_density() +
  theme_bw() 

p3 <- ggplot(data = cleaning, aes(x = guests_included)) +
  geom_density() +
  theme_bw()

p4 <- ggplot(data = cleaning, aes(x = extra_people)) +
  geom_density() +
  theme_bw()

p5 <- ggplot(data = cleaning, aes(x = number_of_reviews)) +
  geom_density() +
  theme_bw()

p6 <- ggplot(data = cleaning, aes(x = review_scores_rating)) +
  geom_density() +
  theme_bw() 

p7 <- ggplot(data = cleaning, aes(x = minimum_nights)) +
  geom_density() +
  theme_bw() 

p8 <- ggplot(data = cleaning, aes(x = accommodates)) +
  geom_density() +
  theme_bw()

p9 <- ggplot(data = cleaning, aes(x = beds)) +
  geom_density() +
  theme_bw()

p10 <- ggplot(data = cleaning, aes(x = bathrooms)) +
  geom_density() +
  theme_bw()

p11 <- ggplot(data = cleaning, aes(x = bedrooms)) +
  geom_density() +
  theme_bw()

p1 + p2 + p3 + p4 + p5 + p6 + p7 + p8 + p9 + p10 + p11

#rescale some of the axis to improve readability

p1a <- ggplot(data = cleaning, aes(x = price)) +
  geom_density() +
  xlim(0, 10000) +
  theme_bw() 

p2a <- ggplot(data = cleaning, aes(x = cleaning_fee)) +
  geom_density() +
  xlim(0, 300) +
  theme_bw() 

p3a <- ggplot(data = cleaning, aes(x = guests_included)) +
  geom_density() +
  xlim(0, 8) +
  theme_bw()

p4a <- ggplot(data = cleaning, aes(x = extra_people)) +
  geom_density() +
  xlim(0, 400) +
  theme_bw()

p5a <- ggplot(data = cleaning, aes(x = number_of_reviews)) +
  geom_density() +
  xlim(0, 100) +
  theme_bw()

p6a <- ggplot(data = cleaning, aes(x = review_scores_rating)) +
  geom_density() +
  xlim(0, 100) +
  theme_bw() 

p7a <- ggplot(data = cleaning, aes(x = minimum_nights)) +
  geom_density() +
  xlim(0, 150) +
  theme_bw() 

p8a <- ggplot(data = cleaning, aes(x = accommodates)) +
  geom_density() +
  theme_bw()

p9a <- ggplot(data = cleaning, aes(x = beds)) +
  geom_density() +
  xlim(0, 20) +
  theme_bw()

p10a <- ggplot(data = cleaning, aes(x = bathrooms)) +
  geom_density() +
  xlim(0, 20) +
  theme_bw()

p11a <- ggplot(data = cleaning, aes(x = bedrooms)) +
  geom_density() +
  xlim(0, 15) +
  theme_bw()

p1a + p2a + p3a + p4a + p5a + p6a + p7a + p8a + p9a + p10a + p11a
```
> Notes on distributions of numerical variables

```{r, fig.width=15, fig.height=15}

# using ggpairs to plot a correlation matrix
data_cleaned %>% 
  select(c(price, cleaning_fee, guests_included, 
           extra_people, number_of_reviews, review_scores_rating, 
           minimum_nights, accommodates, beds, bathrooms, bedrooms, security_deposit)
         ) %>% 
    ggpairs()

```
> Notable correlations with price are:
1. Accomodates (number of people the listing can accomodate)
2. Bedrooms (number of bedrooms at the listing)
3. Bathrooms (number of bathrooms at the listing)
4. Beds (number of beds at the listing)
5. Cleaning fee (additional flat cleaning fee)
6. Guests included (number of guests included in the price and exempt from <extra_people> fee)
7. Extra People (charge per night for each person over the <guests_included>)

> Notable correlations between variables:
1. Accomodates/Beds/Bathrooms/Bedrooms/ - the greater the number of rooms, the greater the number of guests it can accommodate

We're figuring out what types of properties we're dealing with
```{r}

data_cleaned %>% 
  # Counting the frequency of property types
  count(property_type) %>% 
  # Arranging them into descending order by frequency
  arrange(desc(n))

```

We're now classifying different types of properties into 5 groups - the 4 most prominent ones and remaining smaller categories labeled as 'Other'.

```{r}

cleaning <- data_cleaned %>%
      # creating a new variable 'prop_type_simplified' that groups property types into one of 5 categories. For example, "Boutique hotel" will now come under "Other"
  mutate(prop_type_simplified = case_when(
    property_type %in% c("Apartment","Condominium", "House","Loft") ~ property_type, 
    TRUE ~ "Other"
  ))
```

Plotting property types, room types, super host status and cancellation policy, to analyse their distribution. 

```{r}

# using patchwork to plot distribution of different variables
p12 <- ggplot(data = cleaning, aes(x = prop_type_simplified)) +
  geom_bar() +
  theme_bw()

p13 <- ggplot(data = cleaning, aes(x = room_type)) +
  geom_bar() +
  theme_bw()

p14 <- ggplot(data = cleaning, aes(x = host_is_superhost)) +
  geom_bar() +
  theme_bw()

p15 <- ggplot(data = cleaning, aes(x = cancellation_policy)) +
  geom_bar() +
  theme_bw()

p12 + p13 + p14 + p15
```



```{r}

# we use log to transform the highly skewed minimum_nights into more of a normal distribution
cleaning %>% 
  ggplot() +
  geom_density(aes(x = minimum_nights)) +
  scale_x_log10()
cleaning

# arranging listings by minimum_nights
cleaning %>% 
  count(minimum_nights) %>% 
  arrange(desc(n))

# calculating summary statistics for the distribution of minimum_nights
favstats(data = cleaning , ~ minimum_nights) %>% 
  kbl() %>% 
  kable_styling()
```

**From the above, we can infer the following -**
+ The most common values for 'minimum nights' are 1 to 3 nights as they account for 92.1% of total listings. The next biggest category is '30 minimum nights' (2.26% of total listings)
+ 30 minimum nights seem rather strange - maybe the people booking the Airbnbs are visiting Beijing for reasons other than leisure/ travel. For example, they may prefer Airbnbs as a budget friendly alternative to hotels for longer stays intended for business-related work, etc.
+ There are 61 listings for minimum nights of 365 days (1 year) as well which implies that some Airbnbs are more for the purpose of long-term renting or sub-letting.  

## Mapping

```{r}
leaflet(data = filter(cleaning, minimum_nights <= 4)) %>% 
  addProviderTiles("OpenStreetMap.Mapnik") %>% 
  addCircleMarkers(lng = ~longitude, 
                   lat = ~latitude, 
                   radius = 1, 
                   fillColor = "blue", 
                   fillOpacity = 0.4, 
                   popup = ~listing_url,
                   label = ~property_type)
```

## Regression Analysis

```{r, Options(scipen = 999), fig.width=10, fig.height =15}

regression_data <-  cleaning %>% 
  # filter for minimum nights at most 4
  filter(minimum_nights<=4) %>% 
  # New variable that computes the price of 2 people booking an Airbnb for 4 nights
  # Note: extra_people charge per 1 extra person applied per night when no. of guests > guests_included
  mutate(price_for_4_notlog = case_when(
      guests_included < 2 ~ cleaning_fee + (4 * (price + extra_people)),
      TRUE ~ cleaning_fee + (4 * price)
    )
  ) %>% 
  mutate(
    price_4_nights = log(price_for_4_notlog + 0.00001)  #searchable
  )

regression_data

# ggplot for price of four nights
ggplot(data = regression_data, aes(x = price_for_4_notlog)) +
  geom_histogram() +
  xlim(0, 40000)

# ggplot for log of price of four nights
ggplot(data = regression_data, aes(x = price_4_nights)) +
  geom_density() 
      # we use loggy-loggy to effectively change the case from a unit change to a percentage change

# look at cleaned data for regression models
glimpse(regression_data)

```

### Building Linear Regression Models

```{r}

# model 1 with a few variables - reviews and property types
model1 <- lm(price_4_nights ~ 
               prop_type_simplified + number_of_reviews + review_scores_rating,
             regression_data)

model1 %>% tidy(conf.int=TRUE) %>% 
  kbl() %>% 
  kable_styling()

model1 %>% glance() %>% 
  kbl() %>% 
  kable_styling()
```

Here, property type is a categorical variable - it has five categories and therefore makes up 4 dummy variables in the regression model. For example, for 'House', `prop_type_simplifiedHouse` = 1 (`prop_type_simplifiedCondominium` = 0 and `prop_type_simplifiedOther` = 0) and the intercept term would be ~7.11. The intercept term for 'Apartment' would be ~6.91.

Other variables such as `number_of_reviews` and `review_scores_rating` are statistically significant and explain the variation in `price_4_nights`, however, a point worth noting is that additional `number_of_reviews` do not lead to an increase in cost for 4 nights as the reviews may not necessarily be good reviews. On the other hand, `review_scores_rating` have a positive effect on price for 4 nights which means that properties with a higher score/ rating would cost more.  


```{r}
model2 <- lm(price_4_nights ~ 
               prop_type_simplified + number_of_reviews + review_scores_rating + room_type, 
             regression_data)
model2 %>% tidy(conf.int=TRUE)
model2 %>% glance()
```

> The following variables are statistically insignificant:
1. prop_type_simplifiedCondominium
1. prop_type_simplifiedLoft
1. prop_type_simplifiedServiced apartment
1. review_scores_rating

## comparing model 1 and model 2
```{r}
huxreg(model1, model2,
       statistics = c('#observations' = 'nobs', 
                      'R squared' = 'r.squared', 
                      'Adj. R Squared' = 'adj.r.squared', 
                      'Residual SE' = 'sigma'), 
       bold_signif = 0.05, 
       stars = NULL
) %>% 
  set_caption('Comparison of models')
```

> interpretation of the coefficients of review scores rating and prop_type_simplified with respect to price_for_4_notlog

## adding more variables  

```{r}
#
model3 <- lm(price_4_nights ~ prop_type_simplified + number_of_reviews + review_scores_rating + room_type + bedrooms + bathrooms + beds + accommodates , 
             regression_data
            )

model3 %>% tidy(conf.int=TRUE)
model3 %>% glance()

# excluded beds but realised let's keep it
# model4 <- lm(price_4_nights ~ prop_type_simplified + number_of_reviews + review_scores_rating + room_type + bedrooms + bathrooms + accommodates , 
#              regression_data
#             )
# 
# model4 %>% tidy(conf.int=TRUE)
# model4 %>% glance()
```
> hypothesize that being a super host would significantly impact price of 4 nights 

```{r}
# superhost or not
model5 <- lm(price_4_nights ~ prop_type_simplified + number_of_reviews + review_scores_rating + room_type + bedrooms + bathrooms + beds + accommodates + host_is_superhost, 
             regression_data
            )

model5 %>% tidy(conf.int=TRUE)
model5 %>% glance()
```
> our hypothesis is rejected as the variable is insignificant. drop host_is_superhost, does not matter heheh. add some logic as to why people visiting Beijing don't care if their host is a superhost. 

```{r}
# We know that superhost is not relevant, however, is it relevant if its intertwined with the number of reviews?
model6 <- lm(price_4_nights ~ prop_type_simplified + number_of_reviews + review_scores_rating + room_type + bedrooms + bathrooms + beds + accommodates + host_is_superhost*number_of_reviews, 
             regression_data
            )

model6 %>% tidy(conf.int=TRUE)
model6 %>% glance()
```
> Nope

```{r}
# We know that superhost is not relevant, however, is it relevant if its intertwined with the review ratings?
model7 <- lm(price_4_nights ~ prop_type_simplified + number_of_reviews + review_scores_rating + room_type + bedrooms + bathrooms + beds + accommodates + host_is_superhost*review_scores_rating, 
             regression_data
            )

model7 %>% tidy(conf.int=TRUE)
model7 %>% glance()
```
> Nope

next variable 

```{r}
model8 <- lm(price_4_nights ~ prop_type_simplified + number_of_reviews + review_scores_rating + room_type + bedrooms + bathrooms + beds + accommodates + is_location_exact, 
             regression_data
            )

model8 %>% tidy(conf.int=TRUE)
model8 %>% glance()
```

We are missing the neighbour stuff

```{r}
# model9 <- lm(price_4_nights ~ prop_type_simplified + number_of_reviews + review_scores_rating + room_type + bedrooms + bathrooms + beds + accommodates + is_location_exact + cancellation_policy,
#              regression_data
#             )
# 
# model9 %>% tidy(conf.int=TRUE)
# model9 %>% glance()
```

We now add the cancellation policy stuff

```{r}
model10 <- lm(price_4_nights ~ prop_type_simplified + number_of_reviews + review_scores_rating + room_type + bedrooms + bathrooms + beds + accommodates + is_location_exact + cancellation_policy,
             regression_data
            )

model10 %>% tidy(conf.int=TRUE)
model10 %>% glance()
```
> Cancelation policy does not seem to significantly affect the price

```{r}
huxreg(model3, model4, model5, model8, model10,
       statistics = c('#observations' = 'nobs', 
                      'R squared' = 'r.squared', 
                      'Adj. R Squared' = 'adj.r.squared', 
                      'Residual SE' = 'sigma'), 
       bold_signif = 0.05, 
       stars = NULL
) %>% 
  set_caption('Comparison of models')
```

```{r}

# regression_data %>% 
#   select(c(price_4_nights, 
#            review_scores_cleanliness, security_deposit)) %>% 
# ggpairs()

model11 <- lm(price_4_nights ~ prop_type_simplified + number_of_reviews + review_scores_rating + room_type + bedrooms + bathrooms + beds + accommodates + is_location_exact + cancellation_policy + review_scores_cleanliness, 
             regression_data
            )

model11 %>% tidy(conf.int=TRUE)
model11 %>% glance()

model12 <- lm(price_4_nights ~ prop_type_simplified + number_of_reviews + review_scores_rating + room_type + bedrooms + bathrooms + beds + accommodates + is_location_exact + cancellation_policy + instant_bookable,
             regression_data
            )

model12 %>% tidy(conf.int=TRUE)
model12 %>% glance()

model13 <- lm(price_4_nights ~ prop_type_simplified + number_of_reviews + review_scores_rating + room_type + bedrooms + bathrooms + beds + accommodates + is_location_exact + security_deposit,
             regression_data
            )

model13 %>% tidy(conf.int=TRUE)
model13 %>% glance()

#################
huxreg(model11, model12, model13,
       statistics = c('#observations' = 'nobs', 
                      'R squared' = 'r.squared', 
                      'Adj. R Squared' = 'adj.r.squared', 
                      'Residual SE' = 'sigma'), 
       bold_signif = 0.05, 
       stars = NULL
) %>% 
  set_caption('Comparison of models')

# 

car::vif(model1)
car::vif(model2)
car::vif(model13)

########### https://www.displayr.com/variance-inflation-factors-vifs/ USE THIS TO EXPLAIN - ex: beds/baths/accommodates - but none of the VIFs is high enough to suggest collinearity so we're good

```


## Diagnostics, collinearity, summary tables

```{r}

autoplot(model1)

```


reading_week <- regression_data %>% 
  filter(prop_type_simplified=="Apartment", 
         room_type=="Private room", 
         number_of_reviews >=10,
         review_scores_rating >=90)

reading_week

set.seed(6789)

train_test_split <- initial_split(reading_week, prop=0.75)
reading_week_train <- training(train_test_split)
reading_week_test <- testing(train_test_split)

rmse_train <- reading_week_train %>% 
  mutate(
    predictions = predict(model1, .)
  ) %>% 
  summarise(
    sqrt(sum(predictions - price_4_nights)**2/n())) %>% 
  pull()

rmse_train

rmse_test <- reading_week_test %>% 
  mutate(predictions = predict(model1, .)) %>% 
  summarise(
    sqrt(sum(predictions - price_4_nights)**2/n())) %>% 
  pull()

rmse_test

```
