---
title: "Group 13 - Final Project: Beijing"
author: "Study Group 13"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: minty
    highlight: breezedark
    number_sections: yes
    toc: yes
    toc_float: yes
    code_folding: show
---

#Change theme

```{r, setup, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
options(digits = 3)
# default figure size
knitr::opts_chunk$set(
  fig.width=6.75, 
  fig.height=6.75,
  fig.align = "center"
)
```

```{r load-libraries, include=FALSE}
#Using this space to load libraries
library(vroom)
library(dplyr)
library(knitr)
library(mosaic)
library(skimr)
library(ggplot2)
library(GGally)
library(janitor)
library(readr)
library(leaflet)
library(scales)
library(broom)
library(huxtable)
library(car)
library(ggfortify)
library(rsample)
library(ggridges)
library(patchwork)
library(kableExtra)
options('huxtable.knit_print_df' = FALSE)
```

# Studying he Beijing Airbnb Market

First we have to download the data.

```{r weather_data, cache=TRUE}
data <- vroom::vroom("listings.csv.gz") %>% 
  clean_names()
data
```

## Exploratory Data Analysis 

```{r}
# Lets have a look at what we're dealing with!
glimpse(data)
```
> From this output we can see that we have
* There are just over 36 thousand observations (or Airbnb listings) in Beijing in the data set
* There are 106 different variables included in the data
* These variables are a mixture of 'double', 'character', 'logic' and 'date'
* Straightaway we can see that some of our 'price' variables include dollar signs ($) and are down as 'character' variables rather than 'double' variables

Since this is a large data set with a lot going on, we will compute some summary statistics on key variables

```{r}
  listings <- data %>% 
  
  #Lets pick the variables we need
  select(c(price,
           cleaning_fee,
           extra_people,
           room_type,
           property_type,
           number_of_reviews,
           review_scores_rating,
           longitude,
           latitude,
           neighbourhood,
           minimum_nights,
           guests_included,
           bathrooms,
           bedrooms,
           beds,
           accommodates,
           host_is_superhost,
           neighbourhood_cleansed,
           cancellation_policy,
           listing_url,
           is_location_exact,
           security_deposit,
           review_scores_cleanliness,
           instant_bookable,
           is_business_travel_ready
           )
         ) %>% 

  #Removing dollar signs and changing into numerical variables
  mutate(
    price = parse_number(price),
    cleaning_fee = parse_number(cleaning_fee),
    extra_people = parse_number(extra_people),
    security_deposit = parse_number(security_deposit)
  )

listings
```


### Removing Missing Values
```{r}
# Check which variables have lots of missing values (NA's)
listings %>% 
  skim() %>% 
  kbl() %>% 
  kable_styling()

data_cleaned <- listings %>% 
  
  # Handling NA's
  mutate(
    cleaning_fee = case_when(
      is.na(cleaning_fee) ~ 0,
      TRUE ~ cleaning_fee
        ),
    security_deposit = case_when(
      is.na(security_deposit) ~ 0,
      TRUE ~ security_deposit
        )
    )

data_cleaned

data_cleaned %>% 
skim(cleaning_fee) %>% 
  kbl() %>% 
  kable_styling()
```

> Some properties do not have the cleaning fee separately because they include it in the rent price. This way, it is not seen as an "additional cost".
> #Psychology 

### Exploring Correlation Between Variables

```{r}

# Using patchwork to create a visualization of density for all numerical variables
p1 <- ggplot(data = cleaning, aes(x = price)) +
  geom_density() +
  theme_bw() 

p2 <- ggplot(data = cleaning, aes(x = cleaning_fee)) +
  geom_density() +
  theme_bw() 

p3 <- ggplot(data = cleaning, aes(x = guests_included)) +
  geom_density() +
  theme_bw()

p4 <- ggplot(data = cleaning, aes(x = extra_people)) +
  geom_density() +
  theme_bw()

p5 <- ggplot(data = cleaning, aes(x = number_of_reviews)) +
  geom_density() +
  theme_bw()

p6 <- ggplot(data = cleaning, aes(x = review_scores_rating)) +
  geom_density() +
  theme_bw() 

p7 <- ggplot(data = cleaning, aes(x = minimum_nights)) +
  geom_density() +
  theme_bw() 

p8 <- ggplot(data = cleaning, aes(x = accommodates)) +
  geom_density() +
  theme_bw()

p9 <- ggplot(data = cleaning, aes(x = beds)) +
  geom_density() +
  theme_bw()

p10 <- ggplot(data = cleaning, aes(x = bathrooms)) +
  geom_density() +
  theme_bw()

p11 <- ggplot(data = cleaning, aes(x = bedrooms)) +
  geom_density() +
  theme_bw()

p1 + p2 + p3 + p4 + p5 + p6 + p7 + p8 + p9 + p10 + p11

#rescale some of the axis to improve readability

p1a <- ggplot(data = cleaning, aes(x = price)) +
  geom_density() +
  xlim(0, 10000) +
  theme_bw() 

p2a <- ggplot(data = cleaning, aes(x = cleaning_fee)) +
  geom_density() +
  xlim(0, 300) +
  theme_bw() 

p3a <- ggplot(data = cleaning, aes(x = guests_included)) +
  geom_density() +
  xlim(0, 8) +
  theme_bw()

p4a <- ggplot(data = cleaning, aes(x = extra_people)) +
  geom_density() +
  xlim(0, 400) +
  theme_bw()

p5a <- ggplot(data = cleaning, aes(x = number_of_reviews)) +
  geom_density() +
  xlim(0, 100) +
  theme_bw()

p6a <- ggplot(data = cleaning, aes(x = review_scores_rating)) +
  geom_density() +
  xlim(0, 100) +
  theme_bw() 

p7a <- ggplot(data = cleaning, aes(x = minimum_nights)) +
  geom_density() +
  xlim(0, 150) +
  theme_bw() 

p8a <- ggplot(data = cleaning, aes(x = accommodates)) +
  geom_density() +
  theme_bw()

p9a <- ggplot(data = cleaning, aes(x = beds)) +
  geom_density() +
  xlim(0, 20) +
  theme_bw()

p10a <- ggplot(data = cleaning, aes(x = bathrooms)) +
  geom_density() +
  xlim(0, 20) +
  theme_bw()

p11a <- ggplot(data = cleaning, aes(x = bedrooms)) +
  geom_density() +
  xlim(0, 15) +
  theme_bw()

p1a + p2a + p3a + p4a + p5a + p6a + p7a + p8a + p9a + p10a + p11a
```
> Notes on distributions of numerical variables

```{r}
data_numerical <- data_cleaned %>% 
  select(c(price, cleaning_fee, guests_included, extra_people, number_of_reviews, review_scores_rating, minimum_nights, accommodates, beds, bathrooms, bedrooms)) %>% 
    ggpairs() +
  theme_bw()

data_numerical
```
> Notable correlations with price are:
1. Accomodates (number of people the listing can accomodate)
1. Bedrooms (number of bedrooms at the listing)
1. Bathrooms (number of bathrooms at the listing)
1. Beds (number of beds at the listing)
1. Cleaning fee (additional flat cleaning fee)
1. Guests included (number of guests included in the price and exempt from <extra_people> fee)
1. Extra People (charge per night for each person over the <guests_included>)

>Notable correlations between variables:
1. Accomodates/Beds/Bathrooms/Bedrooms/ - this makes sense because...????
1. 

We're figuring out what types of properties we're dealing with
```{r}
data_cleaned %>% 
  
  # Counting the frequency of property types
  count(property_type) %>% 
  
  # Arranging them into descending order by frequency
  arrange(desc(n))

```

We're now classifying into 6 different groups such that we group the smaller categories under 'other'.

```{r}
cleaning <- data_cleaned %>%
  # Creating a new variable that groups the property types into one of 5 categories to group together the smaller types of properties.
  # For example, "Boutique hotel" will now come under "Other"
  mutate(prop_type_simplified = case_when(
    property_type %in% c("Apartment","Condominium", "House","Loft") ~ property_type, 
    TRUE ~ "Other"
  ))
  # %>%
  # count(property_type, prop_type_simplified) %>%
  # arrange(desc(n))
  
p12 <- ggplot(data = cleaning, aes(x = prop_type_simplified)) +
  geom_bar() +
  theme_bw()

p13 <- ggplot(data = cleaning, aes(x = room_type)) +
  geom_bar() +
  theme_bw()

p14 <- ggplot(data = cleaning, aes(x = host_is_superhost)) +
  geom_bar() +
  theme_bw()

p15 <- ggplot(data = cleaning, aes(x = cancellation_policy)) +
  geom_bar() +
  theme_bw()

p12 + p13 + p14 + p15
```



```{r}

# We want to use log to transform our data into a more normal looking distribution of data

cleaning %>% 
  #filter(minimum_nights <= 4) %>% 
  ggplot() +
  geom_density(aes(x = minimum_nights)) +
  scale_x_log10()

cleaning

cleaning %>% 
  count(minimum_nights) %>% 
  arrange(desc(n))

favstats(data = cleaning , ~ minimum_nights) %>% 
  kbl() %>% 
  kable_styling()
```

What are the most common values for the variable minimum_nights?
Is there any value among the common values that stands out?
What is the likely intended purpose for Airbnb listings with this seemingly unusual value for minimum_nights?
Filter the airbnb data so that it only includes observations with minimum_nights <= 4

> The most common values are between 1 to 3 nights.

> Minimum nights over 30 days is rather strange as by this point you're no longer looking to be a tourist and rather live there

>

## Mapping

```{r}
leaflet(data = filter(cleaning, minimum_nights <= 4)) %>% 
  addProviderTiles("OpenStreetMap.Mapnik") %>% 
  addCircleMarkers(lng = ~longitude, 
                   lat = ~latitude, 
                   radius = 1, 
                   fillColor = "blue", 
                   fillOpacity = 0.4, 
                   popup = ~listing_url,
                   label = ~property_type)
```

## Regression Analysis

```{r, Options(scipen = 999), fig.width=10, fig.height =15}

regression_data <-  cleaning %>% 
  # New variable that computes the price of 2 people sleeping in a ... for 4 nights
  # Note that the extra people charge is applied per night when number of guests exceed the guests included variable
  # aka if its less than 2
  mutate(price_4_nights = case_when(
      guests_included < 2 ~ cleaning_fee + (4 * (price + extra_people)),
      TRUE ~ cleaning_fee + (4 * price)
    )
  ) %>% 
  mutate(
    price_4_night = log(price_4_nights)  #searchable
  )

regression_data

# ggplot for price_4_nights
ggplot(data = regression_data, aes(x = price_4_nights)) +
  geom_histogram() +
  xlim(0, 40000)

# ggplot for log of price_4_nights
ggplot(data = regression_data, aes(x = price_4_night)) +
  geom_density() 

# We use loggy-loggy because we effectively change the case from a unit change to a percent change

# ggpairs for correlation
glimpse(regression_data)

regression_data %>% 
  select(-c(room_type, property_type, longitude, latitude, neighbourhood, neighbourhood_cleansed, cancellation_policy, listing_url, prop_type_simplified)) %>% 
  ggpairs()
```
> Johanna's writing about ggpairs

```{r}
model1 <- lm(data = regression_data, price_4_night ~ prop_type_simplified + number_of_reviews + review_scores_rating)
model1 %>% tidy(conf.int=TRUE)
model1 %>% glance() %>% 
  kbl() %>% 
  kable_styling()
```

> The following variables are statistically insignificant:
1. prop_type_simplifiedCondominium
1. prop_type_simplifiedLoft
1. review_scores_rating


```{r}
model2 <- lm(price_4_night ~ prop_type_simplified + number_of_reviews + review_scores_rating + room_type, regression_data)
model2 %>% tidy(conf.int=TRUE)
model2 %>% glance()
```

> The following variables are statistically insignificant:
1. prop_type_simplifiedCondominium
1. prop_type_simplifiedLoft
1. prop_type_simplifiedServiced apartment
1. review_scores_rating

## comparing model 1 and model 2
```{r}
huxreg(model1, model2,
       statistics = c('#observations' = 'nobs', 
                      'R squared' = 'r.squared', 
                      'Adj. R Squared' = 'adj.r.squared', 
                      'Residual SE' = 'sigma'), 
       bold_signif = 0.05, 
       stars = NULL
) %>% 
  set_caption('Comparison of models')
```

> interpretation of the coefficients of review scores rating and prop_type_simplified with respect to price_4_nights

## adding more variables  

```{r}
#
model3 <- lm(price_4_night ~ prop_type_simplified + number_of_reviews + review_scores_rating + room_type + bedrooms + bathrooms + beds + accommodates , 
             regression_data
            )

model3 %>% tidy(conf.int=TRUE)
model3 %>% glance()

# excluded beds but realised let's keep it
# model4 <- lm(price_4_night ~ prop_type_simplified + number_of_reviews + review_scores_rating + room_type + bedrooms + bathrooms + accommodates , 
#              regression_data
#             )
# 
# model4 %>% tidy(conf.int=TRUE)
# model4 %>% glance()
```
> hypothesize that being a super host would significantly impact price of 4 nights 

```{r}
# superhost or not
model5 <- lm(price_4_night ~ prop_type_simplified + number_of_reviews + review_scores_rating + room_type + bedrooms + bathrooms + beds + accommodates + host_is_superhost, 
             regression_data
            )

model5 %>% tidy(conf.int=TRUE)
model5 %>% glance()
```
> our hypothesis is rejected as the variable is insignificant. drop host_is_superhost, does not matter heheh. add some logic as to why people visiting Beijing don't care if their host is a superhost. 

```{r}
# We know that superhost is not relevant, however, is it relevant if its intertwined with the number of reviews?
model6 <- lm(price_4_night ~ prop_type_simplified + number_of_reviews + review_scores_rating + room_type + bedrooms + bathrooms + beds + accommodates + host_is_superhost*number_of_reviews, 
             regression_data
            )

model6 %>% tidy(conf.int=TRUE)
model6 %>% glance()
```
> Nope

```{r}
# We know that superhost is not relevant, however, is it relevant if its intertwined with the review ratings?
model7 <- lm(price_4_night ~ prop_type_simplified + number_of_reviews + review_scores_rating + room_type + bedrooms + bathrooms + beds + accommodates + host_is_superhost*review_scores_rating, 
             regression_data
            )

model7 %>% tidy(conf.int=TRUE)
model7 %>% glance()
```
> Nope

next variable 

```{r}
model8 <- lm(price_4_night ~ prop_type_simplified + number_of_reviews + review_scores_rating + room_type + bedrooms + bathrooms + beds + accommodates + is_location_exact, 
             regression_data
            )

model8 %>% tidy(conf.int=TRUE)
model8 %>% glance()
```

We are missing the neightbourg stuff

```{r}
# model9 <- lm(price_4_night ~ prop_type_simplified + number_of_reviews + review_scores_rating + room_type + bedrooms + bathrooms + beds + accommodates + is_location_exact + cancellation_policy,
#              regression_data
#             )
# 
# model9 %>% tidy(conf.int=TRUE)
# model9 %>% glance()
```

We now add the cancellation policy stuff

```{r}
model10 <- lm(price_4_night ~ prop_type_simplified + number_of_reviews + review_scores_rating + room_type + bedrooms + bathrooms + beds + accommodates + is_location_exact + cancellation_policy,
             regression_data
            )

model10 %>% tidy(conf.int=TRUE)
model10 %>% glance()
```
> Cancelation policy does not seem to significantly affect the price

```{r}
huxreg(model3, model4, model5, model8, model10,
       statistics = c('#observations' = 'nobs', 
                      'R squared' = 'r.squared', 
                      'Adj. R Squared' = 'adj.r.squared', 
                      'Residual SE' = 'sigma'), 
       bold_signif = 0.05, 
       stars = NULL
) %>% 
  set_caption('Comparison of models')
```

```{r}

# regression_data %>% 
#   select(c(price_4_night, 
#            review_scores_cleanliness, security_deposit)) %>% 
# ggpairs()

model11 <- lm(price_4_night ~ prop_type_simplified + number_of_reviews + review_scores_rating + room_type + bedrooms + bathrooms + beds + accommodates + is_location_exact + cancellation_policy + review_scores_cleanliness, 
             regression_data
            )

model11 %>% tidy(conf.int=TRUE)
model11 %>% glance()

model12 <- lm(price_4_night ~ prop_type_simplified + number_of_reviews + review_scores_rating + room_type + bedrooms + bathrooms + beds + accommodates + is_location_exact + cancellation_policy + instant_bookable,
             regression_data
            )

model12 %>% tidy(conf.int=TRUE)
model12 %>% glance()

model13 <- lm(price_4_night ~ prop_type_simplified + number_of_reviews + review_scores_rating + room_type + bedrooms + bathrooms + beds + accommodates + is_location_exact + security_deposit,
             regression_data
            )

model13 %>% tidy(conf.int=TRUE)
model13 %>% glance()

#################
huxreg(model11, model12, model13,
       statistics = c('#observations' = 'nobs', 
                      'R squared' = 'r.squared', 
                      'Adj. R Squared' = 'adj.r.squared', 
                      'Residual SE' = 'sigma'), 
       bold_signif = 0.05, 
       stars = NULL
) %>% 
  set_caption('Comparison of models')

# 

car::vif(model1)
car::vif(model2)
car::vif(model13)

########### https://www.displayr.com/variance-inflation-factors-vifs/ USE THIS TO EXPLAIN - ex: beds/baths/accommodates - but none of the VIFs is high enough to suggest collinearity so we're good

```


## Diagnostics, collinearity, summary tables

```{r}

autoplot(model1)

```
```{r}

reading_week <- regression_data %>% 
  filter(prop_type_simplified=="Apartment", 
         room_type=="Private room", 
         number_of_reviews >=10,
         review_scores_rating >=90)

reading_week

set.seed(6789)

train_test_split <- initial_split(reading_week, prop=0.75)
reading_week_train <- training(train_test_split)
reading_week_test <- testing(train_test_split)

rmse_train <- reading_week_train %>% 
  mutate(
    predictions = predict(model1, .)
  ) %>% 
  summarise(
    sqrt(sum(predictions - price_4_night)**2/n())) %>% 
  pull()

rmse_train

rmse_test <- reading_week_test %>% 
  mutate(predictions = predict(model1, .)) %>% 
  summarise(
    sqrt(sum(predictions - price_4_night)**2/n())) %>% 
  pull()

rmse_test

```
